The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2022-02-03 paper/paper.Rmd
related article about "the average Australian doesn't exist" from the Census data analysis

>>>>

This textbook data was used as an example in @ilk2004, and was developed into a case study for use in teaching exploratory data analysis at `r censor_word("Iowa State University")`. The story from modeling the data (and as reported by Singer and Willett) is that wages increase with the length of time in the workforce, higher level of education leads to higher wages, and that race makes a difference, on average. An exploratory analysis reveals however that the individual experience varies a great deal from the overall average. Some individuals experience a decline in wages the longer they are in the workforce, and many experience volatility in their wages.
